%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {TIER Mobility} % Organization
    {Senior Data Scientist} % Job title
    {Berlin, Germany} % Location
    {Jan. 2021 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Acquisition, CRM and pricing analytics (Python, Snowflake, DBT, Looker)}
        \item {Understanding customers with segmentation and customer lifetime
        value modelling (CatBoost, RFM models, Airflow)}
        \item {Interim head of commercial analytics from 2020 December to beginning \
        of March 2021}
      \end{cvitems}
    }

  \cventry
    {TIER Mobility} % Organization
    {Data Scientist} % Job title
    {Berlin, Germany} % Location
    {Feb. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Data ingestion, operational analytics and geographic
        visualizations (Python, ETLeap, AWS, Redshift, DBT, Looker)}
      \end{cvitems}
    }

  \cventry
    {Nordic Healthcare Group} % Organization
    {Data Scientist} % Job title
    {Helsinki, Finland} % Location
    {Feb. 2019 - Feb 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Integrating medical data from multiple hospitals to one database for hospital benchmarking
        (PostgreSQL, Python)}
        \item {Champion for version control, project management tools,
        reproducibility and internal documentation (GitLab, Asana, ClickUp, Docker, Conda)}
      \end{cvitems}
    }

  \cventry
    {Nordic Healthcare Group} % Organization
    {Data Analyst} % Job title
    {Helsinki, Finland} % Location
    {Jan. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems}
        \item {Data processing and interactive visualization for hospital benchmarking
        in internal medicine and emergency care (Power BI, R, Python, PostgreSQL)}
        \item {Discrete-event simulations of hospital processes (Python, SimPy, Plotly, Dash)}
      \end{cvitems}
    }

  \cventry
    {Grey-Hen Oy} % Organization
    {Junior Data Analyst} % Job title
    {Helsinki, Finland} % Location
    {Sep. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Quality control of the automated data gathering and report generation
        for models predicting prizes of used cars (SAS, R, Microsoft SQL Server)}
        \item {Documentation of the data pipelines and datasets}
      \end{cvitems}
    }

  \cventry
    {University of Helsinki} % Organization
    {Teaching Assistant} % Job title
    {Helsinki, Finland} % Location
    {Jan. 2012 - Dec. 2016} % Date(s)
    {
      \begin{cvitems}
        \item {TA in numerous statistical courses at the departments of social
        psychology and statistics (SPSS, R)}
      \end{cvitems}
    }

  \cventry
    {HUS Service} % Organization
    {Medical Typist (Part-Time)} % Job title
    {Helsinki, Finland} % Location
    {Jul. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems}
        \item {Typing doctors' dictations and turning them into medical records and
        other documents, booking medical procedures}
      \end{cvitems}
    }

  \cventry
    {National Institute of Health and Welfare (THL)} % Organization
    {Trainee (Internship)} % Job title
    {Helsinki, Finland} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems}
        \item {Trainee in the unit "Advancing Mental Health" and the unit
        "Mental Health Problems and Substance Abuse Services".
        My duties were analyzing survey results of the mental health situation
        in Lapland and testing the reliability of psychological measurements
        in patients with psychosis. Work was done using statistical programs SPSS and R}
      \end{cvitems}
    }

  \cventry
    {Palmia, City of Helsinki} % Organization
    {Hospital Service Technician} % Job title
    {Helsinki, Finland} % Location
    {Jun. 2009 - Jul. 2009} % Date(s)
    {
      \begin{cvitems}
        \item {Managing mortuary, providing oxygen bottles to wards and transporting
        patients from the wards to treatments and back}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
